### 2016-04-04 chapters/scenarios.tex
added missing questionnaire usage in chapter 4

@@

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{img/img-screenshots.png}
	\caption{Screen shots of the questionnaire dialog while configuring Odoo}
	\label{img-screenshots}
\end{figure}

{\color{red}TODO: Fragebogen}

>>>>

\subsection{Feature Model extraction}

@@

\subsection{Questionnaire Usage}

\begin{figure}
	\includegraphics[width=\columnwidth]{img/img-screenshots.png}
	\caption{Screen captures of the questionnaire dialog configuring an e-commerce website}
	\label{img-screenshots}
\end{figure}

@@

To check the flexibility and usability of the questionnaire, we decided to try it on a sample use case. As Odoo has not implemented a questionnaire of their own yet, we build one based on their website and features from the generated feature model. As a use case, we chose the demand for a e-commerce website for a newly created online-only shop. To start off, the questionnaire shown in Figure~\ref{img-screenshots} asks whether we already use any Odoo components at our company. If we would have pressed "Yes", we could have chosen which one and in the later steps this would be considered. After choosing "No", we are asked which of the Odoo topics interests us, answering it with "Websites" and "Sales". This brings us to a wizard page showing all of the websites we could choose. After selecting "eCommerce" the next page already chose "Accounting" for us, as this was one of the dependencies from the features that were selected in the background when we chose "eCommerce". No matter what we select on the last page, we can no longer press "next", as there is no next Page for us to configure. To get our configuration file we press "Finish", which we could have done any time during the configuration, generating a partial configuration.

The generated configuration file contains 38 features, from which 10 were selected directly and the rest as dependencies. This process could have been done alone with the feature tree, but that would have taken much longer, as there is no sorting and the feature names are not as descriptive as the choices from the questionnaire. Although we probably did not cover all possible cases in our questionnaire doe to the lack of domain knowledge, this sample shows that this use case can be handled comfortably with our questionnaire.
